The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes

### 2019-08-06 paper2_JNLS/paper.tex
NM

%----------------------------------------------------------------------------%
% Hamiltonian
%----------------------------------------------------------------------------%
\subsection{Hamiltonian structure of TKdV}

We introduce the cubic and quadratic Hamiltonian components as
\begin{align}
\Hthree = \frac{1}{6} \int_{-\pi}^{\pi} u^3 \dx	\, , \qquad
\Htwo = \frac{1}{2} \int_{-\pi}^{\pi} u_x^2 \dx	\, .
\end{align}
Then the Hamiltonian of \eqref{dimlessKdV} on each side of the ADC is given by
\begin{equation}
\Ham = C_3 \drat^{-1} \, \Hthree - C_2 \drat \, \Htwo
\end{equation}
where $\drat$ changes value across the ADC. More specifically, there exists an upstream and a downstream Hamiltonian
\begin{align}
&\Hup = C_3 \, \Hthree - C_2 \, \Htwo \\
&\Hdn = C_3 \dratdn^{-1} \, \Hthree - C_2 \dratdn \, \Htwo
\end{align}
$\Hup$ is a conserved quantity for $t<0$ and $\Hdn$ is a conserved quantity for $t>0$. In examining statistical mechanics of this Hamiltonian system, we will appeal to the idea of a {\em mixed microcanonical-canonical} Gibbs ensemble, as originally introduced in \cite{abramov2003hamiltonian} for the Burgers-Hopf system. Specifically, this ensemble is microcanonical in the energy, with a fixed energy value, and it is canonical in the Hamiltonian. By fixing the energy and hence confining to a compact set, this construction avoids the divergence at infinity that would occur for a simple canonical ensemble. The resulting distribution is thus normalizable.
Accordingly, each Hamiltonian $\Ham^{\pm}$ generates a corresponding mixed ensemble, or Gibbs measure given by 
\begin{align}
\Gupdn = C_{\thupdn} \exp(-\thupdn \Hupdn) \delta(\En - \pi)
\end{align}
Here $\theta = \thupdn$ is the inverse temperature and $C_{\theta}$ a constant (inverse of the partition function) that depends on $\theta$. Each measure has corresponding ensemble mean $\mean{}_{\pm}$.

>>>>

WRITE PROJECTION OPERATOR AND TKDV

\vsp{10}
%----------------------------------------------------------------------------%
% Hamiltonian
%----------------------------------------------------------------------------%
\subsection{Hamiltonian structure of TKdV}

In examining statistical mechanics of this Hamiltonian system, we will appeal to the idea of a {\em mixed microcanonical-canonical} Gibbs ensemble, as originally introduced in \cite{abramov2003hamiltonian} for the Burgers-Hopf system. Specifically, this ensemble is microcanonical in the energy, with a fixed energy value, and it is canonical in the Hamiltonian. By fixing the energy and hence confining to a compact set, this construction avoids the divergence at infinity that would occur for a simple canonical ensemble. The resulting distribution is thus normalizable.
Accordingly, each Hamiltonian $\Ham^{\pm}$ generates a corresponding mixed ensemble, or Gibbs measure given by 
\begin{align}
\Gupdn = C_{\thupdn} \exp(-\thupdn \Hupdn) \delta(\En - \pi)
\end{align}
Here $\theta = \thupdn$ is the inverse temperature and $C_{\theta}$ a constant (inverse of the partition function) that depends on $\theta$. Each measure has corresponding ensemble mean $\mean{}_{\pm}$.
